---
editor_options: 
  markdown: 
    wrap: 72
---

# Load tidyverse and palmerpenguins libraries

# Create a ggplot scatter plot using the penguins dataset.

# Plot bill_length_mm on the x-axis and bill_depth_mm on the y-axis.

# Color points by species and use geom_point with size 3.

# Add a minimal theme and clean labels.

```{r}
library("tidyverse")
library("palmerpenguins")
```

# Create a ggplot scatter plot using the penguins dataset.

# Plot bill_length_mm on the x-axis and bill_depth_mm on the y-axis.

# Color points by species and use geom_point with size 3.

# Add a minimal theme and clean labels.

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm
, color = species)) +
  geom_point(size = 3) +
  theme_minimal() +
  labs(title = "Bill Length vs Bill Depth of Penguins",
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)",
       color = "Species")
```

ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm ,
color = species)) + geom_point(size = 3) + theme_minimal() + labs(title
= "Bill Length vs Bill Depth of Penguins", x = "Bill Length (mm)", y =
"Bill Depth (mm)", color = "Species")

# Create a boxplot to visualize the distribution of flipper_length_mm for each species.

# Use geom_boxplot and fill the boxes by species.

```{r}
ggplot(data = penguins, aes(x = species, y = flipper_length_mm,
, fill = species)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Distribution of Flipper Length by Species",
       x = "Species",
       y = "Flipper Length (mm)",
       fill = "Species")
```

ggplot(data = penguins, aes(x = species, y = flipper_length_mm, , fill =
species)) + geom_boxplot() + theme_minimal() + labs(title =
"Distribution of Flipper Length by Species", x = "Species", y = "Flipper
Length (mm)", fill = "Species")

# Create a histogram to visualize the distribution of body_mass_g.

# Use geom_histogram with bins set to 30 and fill the bars by species.

```{r}
ggplot(data = penguins, aes(x = body_mass_g, fill = species)) +
  geom_histogram(bins = 30, alpha = 0.7, position =
 "identity") +
  theme_minimal() +
  labs(title = "Distribution of Body Mass of Penguins",
       x = "Body Mass (g)",
       y = "Count",
       fill = "Species")
```

ggplot(data = penguins, aes(x = body_mass_g, fill = species)) +
geom_histogram(bins = 30, alpha = 0.7, position = "identity") +
theme_minimal() + labs(title = "Distribution of Body Mass of Penguins",
x = "Body Mass (g)", y = "Count", fill = "Species")

usethis::use_git()
